---
title: "hw1"
author: "Chun-Yu Tseng"
date: "2024-01-27"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Table of Contents
- Section 1: Plot the data for each security to check for missing data
  * Information Technology  
    * [ASML](#section-1-1)
    * [CRM](#section-1-2)
  * Engery  
    * [XOM](#section-1-3)
    * [ET](#section-1-4)
  * Real Estate   
    * [NLY](#section-1-5)
    * [PLD](#section-1-6)
- Section 2: Plot candlestick charts for one stock from each sector
   * [ASML in Information Technology](#section-2-1)
   * [NLY in Real Estate](#section-2-2)
   * [XOM in Engery](#section-2-3)
- Section 3: Develop a plot comparing the capital gains by sector
   * [capital gains Plot](#section-3)
- Section 4: Rolling 50-Day and 200-Day Average Price
   * [Avg Plot](#section-4)
- Section 5: Bollinger Bands Plot
   * [Bollinger Bands Plot](#section-5)
   
# ASML {#section-1-1}
```{r ASML}
library(quantmod)
data.ASML <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/ASML.csv",header=TRUE)
head(data.ASML) 
class(data.ASML$Date) 
date <- as.Date(data.ASML$Date,format="%Y-%m-%d")  
head(date)
data.ASML <- cbind(date, data.ASML[,-1])   # -1 deletes the original Date variable
data.ASML <- data.ASML[order(data.ASML$date),]
names(data.ASML)
names(data.ASML) <- paste(c("ASML.Date","ASML.Open","ASML.High","ASML.Low","ASML.Close","ASML.Adjusted","ASML.Volume"))
head(data.ASML)
```
## Checking Data
```{r Checking ASML Data}
plot(data.ASML$ASML.Date,data.ASML$ASML.Close, type = "l")
dim(data.ASML) 
summary(data.ASML)
```
## CRM {#section-1-2}

```{r CRM}
library(quantmod)
data.CRM <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/CRM.csv",header=TRUE)
head(data.CRM) 
class(data.CRM$Date) 
date <- as.Date(data.CRM$Date,format="%Y-%m-%d")  
head(date)
data.CRM <- cbind(date, data.CRM[,-1])   # -1 deletes the original Date variable
data.CRM <- data.CRM[order(data.CRM$date),]
names(data.CRM)
names(data.CRM) <- paste(c("CRM.Date","CRM.Open","CRM.High","CRM.Low","CRM.Close","CRM.Adjusted","CRM.Volume"))
head(data.CRM)
```
## Checking Data
```{r Checking CRM Data}
plot(data.CRM$CRM.Date,data.CRM$CRM.Close, type = "l")
dim(data.CRM) 
summary(data.CRM)
```
## NLY {#section-1-5}
```{r}
data.NLY <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/NLY.csv",header=TRUE)
head(data.NLY) 
class(data.NLY$Date) 
date <- as.Date(data.NLY$Date,format="%Y-%m-%d")  
head(date)
data.NLY <- cbind(date, data.NLY[,-1])   # -1 deletes the original Date variable
data.NLY <- data.NLY[order(data.NLY$date),]
names(data.NLY)
names(data.NLY) <- paste(c("NLY.Date","NLY.Open","NLY.High","NLY.Low","NLY.Close","NLY.Adjusted","NLY.Volume"))
head(data.NLY)
```
## Checking Data
```{r Checking NLY Data}
plot(data.NLY$NLY.Date,data.NLY$NLY.Close, type = "l")
dim(data.NLY) 
summary(data.NLY)
```

## PLD {#section-1-6}
```{r PLD}
library(quantmod)
data.PLD <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/PLD.csv",header=TRUE)
head(data.PLD) 
class(data.PLD$Date) 
date <- as.Date(data.PLD$Date,format="%Y-%m-%d")  
head(date)
data.PLD <- cbind(date, data.PLD[,-1])   # -1 deletes the original Date variable
data.PLD <- data.PLD[order(data.PLD$date),]
names(data.PLD)
names(data.PLD) <- paste(c("PLD.Date","PLD.Open","PLD.High","PLD.Low","PLD.Close","PLD.Adjusted","PLD.Volume"))
head(data.PLD)
```
## Checking Data
```{r Checking PLD Data}
plot(data.PLD$PLD.Date,data.PLD$PLD.Close, type = "l")
dim(data.PLD) 
summary(data.PLD)
```


## XOM {#section-1-3}
```{r XOM}
library(quantmod)
data.XOM <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/XOM.csv",header=TRUE)
head(data.XOM) 
class(data.XOM$Date) 
date <- as.Date(data.XOM$Date,format="%Y-%m-%d")  
head(date)
data.XOM <- cbind(date, data.XOM[,-1])   # -1 deletes the original Date variable
data.XOM <- data.XOM[order(data.XOM$date),]
names(data.XOM)
names(data.XOM) <- paste(c("XOM.Date","XOM.Open","XOM.High","XOM.Low","XOM.Close","XOM.Adjusted","XOM.Volume"))
head(data.XOM)
```
## Checking Data
```{r Checking XOM Data}
plot(data.XOM$XOM.Date,data.XOM$XOM.Close, type = "l")
dim(data.XOM) 
summary(data.XOM)
```
## ET {#section-1-4}
```{r ET}
library(quantmod)
data.ET <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/ET.csv",header=TRUE)
head(data.ET) 
class(data.ET$Date) 
date <- as.Date(data.ET$Date,format="%Y-%m-%d")  
head(date)
data.ET <- cbind(date, data.ET[,-1])   # -1 deletes the original Date variable
data.ET <- data.ET[order(data.ET$date),]
names(data.ET)
names(data.ET) <- paste(c("ET.Date","ET.Open","ET.High","ET.Low","ET.Close","ET.Adjusted","ET.Volume"))
head(data.ET)
```
## Checking Data
```{r Checking ET Data}
plot(data.ET$ET.Date,data.ET$ET.Close, type = "l")
dim(data.ET) 
summary(data.ET)
```
## Candle stick from ASML in the Information Technology sector {#section-2-1}
``` {r}
wk <- data.ASML
data.weekly <- to.weekly(wk)
data.weekly[c(1:3,nrow(data.weekly)),]
OHLC <- data.weekly[-1,-6]
ASML.ohlc <- as.quantmod.OHLC(OHLC,col.names=c("Open","High","Low","Close","Volume"))
ASML.ohlc[c(1:3,nrow(ASML.ohlc)),]
chartSeries(ASML.ohlc,name="ASML OHLC")
```

## Candle stick from NLY in the Real Estate sector {#section-2-2}
``` {r}
wk <- data.NLY
data.weekly <- to.weekly(wk)
data.weekly[c(1:3,nrow(data.weekly)),]
OHLC <- data.weekly[-1,-6]
NLY.ohlc <- as.quantmod.OHLC(OHLC,col.names=c("Open","High","Low","Close","Volume"))
NLY.ohlc[c(1:3,nrow(NLY.ohlc)),]
chartSeries(NLY.ohlc,name="NLY OHLC")
```

# Candle stick from XOM in the Engery sector{#section-2-3}
``` {r}
wk <- data.XOM
data.weekly <- to.weekly(wk)
data.weekly[c(1:3,nrow(data.weekly)),]
OHLC <- data.weekly[-1,-6]
XOM.ohlc <- as.quantmod.OHLC(OHLC,col.names=c("Open","High","Low","Close","Volume"))
XOM.ohlc[c(1:3,nrow(XOM.ohlc)),]
chartSeries( XOM.ohlc,name="XOM OHLC")
```

## Develop a plot comparing the capital gains by sector{#section-3}
```{r Captial gain in each sector}
#ASML
data.ASML <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/ASML.csv",header=TRUE)
data.CRM <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/CRM.csv",header=TRUE)
data.NLY <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/NLY.csv",header=TRUE)
data.PLD <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/PLD.csv",header=TRUE)
data.XOM <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/XOM.csv",header=TRUE)
data.ET <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/ET.csv",header=TRUE)


#only 2009 
data.ASML <- data.ASML[-c(1:505, 757:nrow(data.ASML)), ]
data.CRM <- data.CRM[-c(1:505, 757:nrow(data.CRM)), ]
data.NLY <- data.NLY[-c(1:505, 757:nrow(data.NLY)), ]
data.PLD <- data.PLD[-c(1:505, 757:nrow(data.PLD)), ]
data.XOM <- data.XOM[-c(1:505, 757:nrow(data.XOM)), ]
data.ET <- data.ET[-c(1:505, 757:nrow(data.ET)), ]

date <- as.Date(data.ASML$Date,format="%Y-%m-%d")  
#date <- as.Date(data.CRM$Date,format="%Y-%m-%d")  

data.ASML <- cbind(date, data.ASML[,-1])
data.CRM <- cbind(date, data.CRM[,-1])
data.NLY <- cbind(date, data.NLY[,-1])
data.PLD <- cbind(date, data.PLD[,-1])
data.XOM <- cbind(date, data.XOM[,-1])
data.ET <- cbind(date, data.ET[,-1])


data.ASML <- data.ASML[order(data.ASML$date),]
data.CRM <- data.CRM[order(data.CRM$date),]
data.NLY <- data.NLY[order(data.NLY$date),]
data.PLD <- data.PLD[order(data.PLD$date),]
data.XOM <- data.XOM[order(data.XOM$date),]
data.ET <- data.ET[order(data.ET$date),]


data.ASML <- xts(data.ASML[,2:7],order.by=data.ASML[,1])
data.CRM <- xts(data.CRM[,2:7],order.by=data.CRM[,1])
data.NLY <- xts(data.NLY[,2:7],order.by=data.NLY[,1])
data.PLD <- xts(data.PLD[,2:7],order.by=data.PLD[,1])
data.XOM <- xts(data.XOM[,2:7],order.by=data.XOM[,1])
data.ET <- xts(data.ET[,2:7],order.by=data.ET[,1])


names(data.ASML) <- paste(c("ASML.Open","ASML.High","ASML.Low","ASML.Close","ASML.Adjusted","ASML.Volume"))
names(data.CRM) <- paste(c("CRM.Open","CRM.High","CRM.Low","CRM.Close","CRM.Adjusted","CRM.Volume"))
names(data.NLY) <- paste(c("NLY.Open","NLY.High","NLY.Low","NLY.Close","NLY.Adjusted","NLY.Volume"))
names(data.PLD) <- paste(c("PLD.Open","PLD.High","PLD.Low","PLD.Close","PLD.Adjusted","PLD.Volume"))
names(data.XOM) <- paste(c("XOM.Open","XOM.High","XOM.Low","XOM.Close","XOM.Adjusted","XOM.Volume"))
names(data.ET) <- paste(c("ET.Open","ET.High","ET.Low","ET.Close","ET.Adjusted","ET.Volume"))


Close.Prices <- cbind(data.ASML$ASML.Close, data.CRM$CRM.Close,
                      data.NLY$NLY.Close, data.PLD$PLD.Close,
                      data.XOM$XOM.Close, data.ET$ET.Close)

Close.Prices[c(1:3,nrow(Close.Prices)),]

multi.df <- cbind(index(Close.Prices),data.frame(Close.Prices))

names(multi.df) <- paste(c("date","ASML","CRM", "NLY", "PLD", "XOM", "ET"))

rownames(multi.df) <- seq(1,nrow(multi.df),1)

multi.df[c(1:3,nrow(multi.df)),]

#Sector calculate
multi.df$InformationTechnology.idx <- (multi.df$CRM/multi.df$CRM[1] + multi.df$ASML/multi.df$ASML[1])/2
multi.df$RealEstate.idx <- (multi.df$NLY/multi.df$NLY[1] + multi.df$PLD/multi.df$PLD[1])/2
multi.df$Energy.idx <- (multi.df$XOM/multi.df$XOM[1] + multi.df$ET/multi.df$ET[1])/2

multi.df[c(1:3,nrow(multi.df)),]    
#plot
plot(x=multi.df$date,
     y=multi.df$InformationTechnology.idx,
     type="l",
     xlab="Date",
     ylab="Value of Investment ($)",
     col="#435792",
     lty=1,
     lwd=2,
     main="Value of $1 Investment")+
lines(x=multi.df$date,
      y=multi.df$RealEstate.idx,
      type="l",
      col="#393f4f",
      lwd=1)+
lines(x=multi.df$date,
      y=multi.df$Energy.idx,
      type="l",
      col="#bdaa8a",
      lwd=1)+
abline(h=1,lty=1,col="black")
legend("topleft",
       c("Information Technology", "Real Estate", "Energy"),
       col = c("#435792", "#393f4f", "#bdaa8a"),
       lty = c(1, 1, 1),
       lwd = c(2, 1, 1))
```

## Plot the SMA in 50 days and 200 days{#section-4}
### Picking Engery sector to analyze
```{r SMA}
library(ggplot2)
data.XOM <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/XOM.csv",header=TRUE)
data.ET <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/ET.csv",header=TRUE)


colnames(data.XOM)[1] <- "Date"
Energy.sma <- data.frame(data.XOM[, 1])
#Calculate the total of the Enegery
Energy.sma[, 2:7] <- data.XOM[, 2:7] + data.ET[, 2:7]
colnames(Energy.sma)[1] <- "Date"
Energy.sma[c(1:3,nrow(Energy.sma)),]

Energy.sma$sma50 <- zoo::rollmeanr(Energy.sma$Close, k = 50, fill = NA)
Energy.sma$sma200 <- zoo::rollmeanr(Energy.sma$Close, k = 200, fill = NA)
Energy.sma[c(1:3,nrow(Energy.sma)),] 
Energy.sma$Date <- as.Date(Energy.sma$Date)


Energy.sma <- subset(Energy.sma, Date > as.Date('2007-01-01'))
y.range <- range(Energy.sma[, 1], na.rm = TRUE)

plot(Energy.sma$Date, 
     Energy.sma$Close, type = "l", col = "black", lty = 1, ylim = range(Energy.sma$Close, na.rm = TRUE),
     xlab = "Date", ylab = "Close Price", main = "Close Price Over Time")
     lines(Energy.sma$Date, Energy.sma$sma50, col = "red", lty = 1)
     lines(Energy.sma$Date, Energy.sma$sma200, col = "blue", lty = 2)
     legend("topright", legend = c("Close", "sma50", "sma200"), col = c("black", "red", "blue"), lty = c(1, 1, 2))
```

## Bollinger Bands Plot in my profolio{#section-5}
```{r Bollinger Bands}
data.ASML <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/ASML.csv",header=TRUE)
data.CRM <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/CRM.csv",header=TRUE)
data.NLY <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/NLY.csv",header=TRUE)
data.PLD <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/PLD.csv",header=TRUE)
data.XOM <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/XOM.csv",header=TRUE)
data.ET <- read.csv("/Users/ALEX/Documents/515Project/dataset/2011To2024/ET.csv",header=TRUE)

colnames(data.XOM)[1] <- "Date"
Total.bb <- data.frame(data.XOM[, 1])
#Calculate the total of the Enegery and invest one dollar in each stock
Total.bb$Close <- data.XOM[, 5] + data.ET[, 5] + data.ASML[, 5] + data.CRM[, 5] + data.PLD[, 5] + data.NLY[, 5] 
colnames(Total.bb)[1] <- "Date"
Total.bb[c(1:3,nrow(Total.bb)),]

# Calculate Rolling 20-Day Mean and Std.Dev
Total.bb$avg <- zoo::rollmeanr(Total.bb$Close,k=20,fill = NA)
#Total.bb$sd <- zoo :: rollapply(Total.bb$Close,width = 20,FUN = sd,fill = NA)
Total.bb$sd <- rollapply(Total.bb$Close,width = 20,FUN = sd,fill = NA)

Total.bb[c(1:3,nrow(Total.bb)),]

# Total.Five <- subset(Total.bb, Date > as.Date('2011-01-01'))
Total.Five[c(1:3,nrow(Total.Five)),]

Total.Five$sd2up <- Total.Five$avg+2*Total.Five$sd
Total.Five$sd2down <- Total.Five$avg-2*Total.Five$sd
Total.Five[c(1:3,nrow(Total.Five)),]
Total.Five$Date <- as.Date(Total.Five$Date)

plot(Total.Five$Date,
     Total.Five$Close,
     type = "l", col = "black", lty = 1, ylim = range(Total.Five$Close, na.rm = TRUE),
     xlab = "Date", ylab = "Close Price", main = "Bollinger Bands in my profolio",)
     lines(Energy.sma$Date,y=Total.Five$avg,lty = 1, col="blue")
     lines(Energy.sma$Date,y=Total.Five$sd2up,col="green")
     lines(Energy.sma$Date,y=Total.Five$sd2down,col="red")
     legend("bottomright", legend = c("Price","20-Day Moving Average","Upper Band","Lower Band"),
     col = c("black","blue", "green", "red"), lty = c(1, 1, 1,1))
```