---
title: "Hw2"
author: "Chun-Yu Tseng"
date: "2024-02-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part A – Individual Security Returns  
- Calculate Returns
    * [a Calculate portfolio price returns for the homework period](#section-1-1)
- Dividend reinvestment strategy  
  * [Calculate portfolio total gross returns for the homework period](#section-2-1)  
  * [Calculate portfolio logarithmic gross returns for the homework period](#section-2-2)  
  * [Are the results the same?](#section-2-3)
- [Plot a comparison of Total Price returns and Total Gross returns](#section-2-4)

## Part B – Portfolio Returns
- Use the same investment period and the same stocks
  * [Create an equally-weighted portfolio (rebalance each quarter)](#section-3-1)
  * [Create a value-weighted portfolio (rebalance each quarter)](#section-3-2)


# Calculate portfolio price returns for the homework period {#section-1-1}
The data I choose is ASML, CRM, NLY, XOM, and Calaucte the return in holding each stock for 5 years.
```{r Loading Data and calcuate, echo=FALSE}
library(xts)
library(quantmod)
data.ASML <- read.csv("/Users/ALEX/Documents/workspace_R/515/dataset/ASML.csv",header=TRUE)
data.CRM <- read.csv("/Users/ALEX/Documents/workspace_R/515/dataset/CRM.csv",header=TRUE)
data.NLY <- read.csv("/Users/ALEX/Documents/workspace_R/515/dataset/NLY.csv",header=TRUE)
data.XOM <- read.csv("/Users/ALEX/Documents/workspace_R/515/dataset/XOM.csv",header=TRUE)
#ASML Data
date <- as.Date(data.ASML$Date,format="%Y-%m-%d") 
data.ASML <- cbind(date, data.ASML[,-1])
data.ASML <- data.ASML[order(data.ASML$date),]
data.ASML <- xts(data.ASML[,2:7],order.by=data.ASML[,1])
names(data.ASML) <- paste(c("ASML.Open","ASML.High","ASML.Low","ASML.Close","ASML.Adjusted","ASML.Volume"))
#CRM Data
data.CRM <- cbind(date, data.CRM[,-1])  
data.CRM <- data.CRM[order(data.CRM$date),]
data.CRM <- xts(data.CRM[,2:7],order.by=data.CRM[,1])
names(data.CRM) <- paste(c("CRM.Open","CRM.High","CRML.Low","CRM.Close","CRM.Adjusted","CRM.Volume"))
#NLY Data
data.NLY <- cbind(date, data.NLY[,-1])  
data.NLY <- data.NLY[order(data.NLY$date),]
data.NLY <- xts(data.NLY[,2:7],order.by=data.NLY [,1])
names(data.NLY) <- paste(c("NLY.Open","NLY.High","NLY.Low","NLY.Close","NLY.Adjusted","NLY.Volume"))
#XOM Data
data.XOM <- cbind(date, data.XOM[,-1])  
data.XOM <- data.XOM[order(data.XOM$date),]
data.XOM <- xts(data.XOM[,2:7],order.by=data.XOM[,1])
names(data.XOM) <- paste(c("XOM.Open","XOM.High","XOM.Low","XOM.Close","XOM.Adjusted","XOM.Volume"))
#Mulit all the data

multi <- data.ASML[,5]
multi <- merge(multi,data.CRM[,5])
multi <- merge(multi,data.NLY[,5])
multi <- merge(multi,data.XOM[,5])
multi[c(1:3,nrow(multi)),]
# #Print first and the five years later
period.ret <- multi[c(1,nrow(multi)),]
period.ret
# #Calculate returns and buy each 1 stock
rets <- lapply(period.ret,Delt)
rets <- data.frame(rets)
rets <- rets[2,]*100
names(rets) <- paste(c("ASML","CRM","NLY","XOM"))
rets
ASML_buy <- 27.4
CRM_buy <- 9.01
NLY_buy <- 56.04
XOM_buy<- 74.11
total_price = (ASML_buy + CRM_buy + NLY_buy + XOM_buy)
w.ASML_buy <- ASML_buy/(total_price)
w.CRM_buy <- CRM_buy/(total_price)
w.NLY_buy <- NLY_buy/(total_price)
w.XOM_buy <- XOM_buy/(total_price)
w.ASML_buy
w.CRM_buy
w.NLY_buy
w.XOM_buy
port.ret.4asset <- w.ASML_buy*rets$ASML + w.CRM_buy*rets$CRM + w.NLY_buy*rets$NLY + w.XOM_buy*rets$XOM
sprintf("MY total return is %f" ,port.ret.4asset)
```
# Calculate portfolio price returns for the homework period {#section-2-1}
```{r portfolio total gross returns, echo=FALSE}
i.ASML <- 25000
i.CRM <- 20000
i.NLY <- 30000
i.XOM <- 25000
quantityASML = i.ASML/ASML_buy
quantityCRM = i.CRM/CRM_buy
quantityNLY = i.NLY/NLY_buy
quantityXOM = i.XOM/XOM_buy
totalGross = (data.ASML$ASML.Close[nrow(data.ASML)] * quantityASML +
  data.CRM$CRM.Close[nrow(data.CRM)] * quantityCRM +
  data.NLY$NLY.Close[nrow(data.NLY)] * quantityNLY +
  data.XOM$XOM.Close[nrow(data.XOM)] * quantityXOM) - 100000
sprintf("MY total gross return is %f" , totalGross)
```

# Calculate portfolio logarithmic gross returns for the homework period {#section-2-2}
```{r, echo=FALSE}
multiClose <- data.ASML[,4]
multiClose <- merge(multiClose,data.CRM[,4])
multiClose <- merge(multiClose,data.NLY[,4])
multiClose <- merge(multiClose,data.XOM[,4])
multiClose$ASML.Price.Ret=Delt(multiClose$ASML.Close)
multiClose$CRM.Price.Ret=Delt(multiClose$CRM.Close)
multiClose$NLY.Price.Ret=Delt(multiClose$NLY.Close)
multiClose$XOM.Price.Ret=Delt(multiClose$XOM.Close)
multiClose$Port.Ret=Delt(multiClose$ASML.Close+multiClose$CRM.Close
                          +multiClose$NLY.Close+multiClose$XOM.Close)
multiClose[1:4,]
PortPriceTotlRet<-prod(multiClose$Port.Ret[2:nrow(multiClose),]+1)-1
PortPriceTotlRet
```
# Are the results the same? {#section-2-3}
```{r, echo=FALSE}
multi$ASML.Ret=Delt(multi$ASML.Adjusted)
multi$CRM.Ret=Delt(multi$CRM.Adjusted)
multi$NLY.Ret=Delt(multi$NLY.Adjusted)
multi$XOM.Ret=Delt(multi$XOM.Adjusted)
multi$Total.Ret <- Delt(multi$ASML.Adjusted+multi$CRM.Adjusted + multi$NLY.Adjusted +multi$XOM.Adjusted)
multi$Port.Tot.Ret<- Delt(multi$ASML.Adjusted+multi$CRM.Adjusted + multi$NLY.Adjusted +multi$XOM.Adjusted)
multi$Port.Log.Tot.Ret<-log(multi$Port.Tot.Ret+1)
multi[1:5,]
Difference<-multi$Port.Tot.Ret-multi$Port.Log.Tot.Ret
plot(Difference)
print("The reuslut is a litte differeent betweeen ")
```
# Plot a comparison of Total Price returns and Total Gross returns {#section-2-4}
```{r, echo=FALSE}
multiClose$Port.Ret=Delt(multiClose$ASML.Close+multiClose$CRM.Close + multiClose$NLY.Close +multiClose$XOM.Close)

multiClose[1:4,]

multiClose<-multiClose[-1,]
multiClose<-subset(multiClose,index(multiClose)>"2007-01-01")
multiClose$indexV<-cumprod(multiClose$Port.Ret+1)

multi<-multi[-1,]
multi<-subset(multi,index(multi)>"2007-01-01")
multi$TotalV<-cumprod(multi$Port.Tot.Ret+1)
plot(multiClose$index, type = "l", xlab = "Date", ylab = "Return", main = "Gross Return vs. Total Return")

# Add the second line to the plot
lines(multi$TotalV, col = 'green')

# Add a legend to differentiate between the two lines
legend("topright", legend = c("Gross Return", "Total Return"), col = c("black", "green"), lty = 1)
 
```

# Create an equally-weighted portfolio (rebalance each quarter) {#section-3-1}
```{r, echo=FALSE}
multi_eq <- data.ASML[,5]
multi_eq <- merge(multi_eq,data.CRM[,5])
multi_eq <- merge(multi_eq,data.XOM[,5])
multi_eq <- merge(multi_eq,data.NLY[,5])
multi_eq$ASML.Ret=Delt(multi_eq$ASML.Adjusted)
multi_eq$CRM.Ret=Delt(multi_eq$CRM.Adjusted)
multi_eq$XOM.Ret=Delt(multi_eq$XOM.Adjusted)
multi_eq$NLY.Ret=Delt(multi_eq$NLY.Adjusted)
#Q1
ew.q1 <- subset(multi_eq, index(multi_eq) > "2007-01-01")
ew.q1 <- subset(ew.q1, index(ew.q1) < "2007-03-31")
ew.q1[c(1:4,nrow(ew.q1)),]
ew.q1$ASML <- cumprod(ew.q1$ASML.Ret+1)
ew.q1$CRM <- cumprod(ew.q1$CRM.Ret+1)
ew.q1$XOM <- cumprod(ew.q1$XOM.Ret+1)
ew.q1$NLY <- cumprod(ew.q1$NLY.Ret+1)
ew.q1$EWPort<-(ew.q1$ASML+ew.q1$CRM+ew.q1$XOM+ew.q1$NLY)/4
ew.q1$EWRet<-rbind(ew.q1$EWPort[1]-1,Delt(ew.q1$EWPort)[-1,])
# #Q2
ew.q2 <- subset(multi_eq, index(multi_eq) > "2007-04-01")
ew.q2 <- subset(ew.q2, index(ew.q2) < "2007-06-30")
ew.q2[c(1:4,nrow(ew.q2)),]
ew.q2$ASML <- cumprod(ew.q2$ASML.Ret+1)
ew.q2$CRM <- cumprod(ew.q2$CRM.Ret+1)
ew.q2$XOM <- cumprod(ew.q2$XOM.Ret+1)
ew.q2$NLY <- cumprod(ew.q2$NLY.Ret+1)
ew.q2$EWPort<-(ew.q2$ASML+ew.q2$CRM+ew.q2$XOM+ew.q2$NLY)/4
ew.q2$EWRet<-rbind(ew.q2$EWPort[1]-1,Delt(ew.q2$EWPort)[-1,])
#Q3
ew.q3 <- subset(multi_eq, index(multi_eq) > "2007-07-01")
ew.q3 <- subset(ew.q3, index(ew.q3) < "2007-09-30")
ew.q3[c(1:4,nrow(ew.q3)),]
ew.q3$ASML <- cumprod(ew.q3$ASML.Ret+1)
ew.q3$CRM <- cumprod(ew.q3$CRM.Ret+1)
ew.q3$XOM <- cumprod(ew.q3$XOM.Ret+1)
ew.q3$NLY <- cumprod(ew.q3$NLY.Ret+1)
ew.q3$EWPort<-(ew.q3$ASML+ew.q3$CRM+ew.q3$XOM+ew.q3$NLY)/4
ew.q3$EWRet<-rbind(ew.q3$EWPort[1]-1,Delt(ew.q3$EWPort)[-1,])
# #Q4
ew.q4 <- subset(multi_eq, index(multi_eq) >= "2007-10-01")
ew.q4 <- subset(ew.q4, index(ew.q4) < "2007-12-31")
ew.q4[c(1:4,nrow(ew.q4)),]
ew.q4$ASML <- cumprod(ew.q4$ASML.Ret+1)
ew.q4$CRM <- cumprod(ew.q4$CRM.Ret+1)
ew.q4$XOM <- cumprod(ew.q4$XOM.Ret+1)
ew.q4$NLY <- cumprod(ew.q4$NLY.Ret+1)
ew.q4$EWPort<-(ew.q4$ASML+ew.q4$CRM+ew.q4$XOM+ew.q4$NLY)/4
ew.q4$EWRet<-rbind(ew.q4$EWPort[1]-1,Delt(ew.q4$EWPort)[-1,])
# #Q5
ew.q5 <- subset(multi_eq, index(multi_eq) > "2008-01-01")
ew.q5 <- subset(ew.q5, index(ew.q5) < "2008-03-31")
ew.q5[c(1:4,nrow(ew.q5)),]
ew.q5$ASML <- cumprod(ew.q5$ASML.Ret+1)
ew.q5$CRM <- cumprod(ew.q5$CRM.Ret+1)
ew.q5$XOM <- cumprod(ew.q5$XOM.Ret+1)
ew.q5$NLY <- cumprod(ew.q5$NLY.Ret+1)
ew.q5$EWPort<-(ew.q5$ASML+ew.q5$CRM+ew.q5$XOM+ew.q5$NLY)/4
ew.q5$EWRet<-rbind(ew.q5$EWPort[1]-1,Delt(ew.q5$EWPort)[-1,])
# #Q6
ew.q6 <- subset(multi_eq, index(multi_eq) > "2008-04-01")
ew.q6 <- subset(ew.q6, index(ew.q6) < "2008-06-30")
ew.q6[c(1:4,nrow(ew.q6)),]
ew.q6$ASML <- cumprod(ew.q6$ASML.Ret+1)
ew.q6$CRM <- cumprod(ew.q6$CRM.Ret+1)
ew.q6$XOM <- cumprod(ew.q6$XOM.Ret+1)
ew.q6$NLY <- cumprod(ew.q6$NLY.Ret+1)
ew.q6$EWPort<-(ew.q6$ASML+ew.q6$CRM+ew.q6$XOM+ew.q6$NLY)/4
ew.q6$EWRet<-rbind(ew.q6$EWPort[1]-1,Delt(ew.q6$EWPort)[-1,])
# #Q7
ew.q7 <- subset(multi_eq, index(multi_eq) > "2008-07-01")
ew.q7 <- subset(ew.q7, index(ew.q7) < "2008-09-30")
ew.q7[c(1:4,nrow(ew.q7)),]
ew.q7$ASML <- cumprod(ew.q7$ASML.Ret+1)
ew.q7$CRM <- cumprod(ew.q7$CRM.Ret+1)
ew.q7$XOM <- cumprod(ew.q7$XOM.Ret+1)
ew.q7$NLY <- cumprod(ew.q7$NLY.Ret+1)
ew.q7$EWPort<-(ew.q7$ASML+ew.q7$CRM+ew.q7$XOM+ew.q7$NLY)/4
ew.q7$EWRet<-rbind(ew.q7$EWPort[1]-1,Delt(ew.q7$EWPort)[-1,])
#Q8
ew.q8 <- subset(multi_eq, index(multi_eq) > "2008-10-01")
ew.q8 <- subset(ew.q8, index(ew.q8) < "2008-12-31")
ew.q8[c(1:4,nrow(ew.q8)),]
ew.q8$ASML <- cumprod(ew.q8$ASML.Ret+1)
ew.q8$CRM <- cumprod(ew.q8$CRM.Ret+1)
ew.q8$XOM <- cumprod(ew.q8$XOM.Ret+1)
ew.q8$NLY <- cumprod(ew.q8$NLY.Ret+1)
ew.q8$EWPort<-(ew.q8$ASML+ew.q8$CRM+ew.q8$XOM+ew.q8$NLY)/4
ew.q8$EWRet<-rbind(ew.q8$EWPort[1]-1,Delt(ew.q8$EWPort)[-1,])
#Q9
ew.q9 <- subset(multi_eq, index(multi_eq) > "2009-01-01")
ew.q9 <- subset(ew.q9, index(ew.q9) < "2009-03-31")
ew.q9[c(1:4,nrow(ew.q9)),]
ew.q9$ASML <- cumprod(ew.q9$ASML.Ret+1)
ew.q9$CRM <- cumprod(ew.q9$CRM.Ret+1)
ew.q9$XOM <- cumprod(ew.q9$XOM.Ret+1)
ew.q9$NLY <- cumprod(ew.q9$NLY.Ret+1)
ew.q9$EWPort<-(ew.q9$ASML+ew.q9$CRM+ew.q9$XOM+ew.q9$NLY)/4
ew.q9$EWRet<-rbind(ew.q9$EWPort[1]-1,Delt(ew.q9$EWPort)[-1,])
#Q10
ew.q10 <- subset(multi_eq, index(multi_eq) > "2009-04-01")
ew.q10 <- subset(ew.q10, index(ew.q10) < "2009-06-30")
ew.q10[c(1:4,nrow(ew.q10)),]
ew.q10$ASML <- cumprod(ew.q10$ASML.Ret+1)
ew.q10$CRM <- cumprod(ew.q10$CRM.Ret+1)
ew.q10$XOM <- cumprod(ew.q10$XOM.Ret+1)
ew.q10$NLY <- cumprod(ew.q10$NLY.Ret+1)
ew.q10$EWPort<-(ew.q10$ASML+ew.q10$CRM+ew.q10$XOM+ew.q10$NLY)/4
ew.q10$EWRet<-rbind(ew.q10$EWPort[1]-1,Delt(ew.q10$EWPort)[-1,])
#Q11
ew.q11 <- subset(multi_eq, index(multi_eq) > "2009-07-01")
ew.q11 <- subset(ew.q11, index(ew.q11) < "2009-09-30")
ew.q11[c(1:4,nrow(ew.q11)),]
ew.q11$ASML <- cumprod(ew.q11$ASML.Ret+1)
ew.q11$CRM <- cumprod(ew.q11$CRM.Ret+1)
ew.q11$XOM <- cumprod(ew.q11$XOM.Ret+1)
ew.q11$NLY <- cumprod(ew.q11$NLY.Ret+1)
ew.q11$EWPort<-(ew.q11$ASML+ew.q11$CRM+ew.q11$XOM+ew.q11$NLY)/4
ew.q11$EWRet<-rbind(ew.q11$EWPort[1]-1,Delt(ew.q11$EWPort)[-1,])
#Q12
ew.q12 <- subset(multi_eq, index(multi_eq) > "2009-10-01")
ew.q12 <- subset(ew.q12, index(ew.q12) < "2009-12-31")
ew.q12[c(1:4,nrow(ew.q12)),]
ew.q12$ASML <- cumprod(ew.q12$ASML.Ret+1)
ew.q12$CRM <- cumprod(ew.q12$CRM.Ret+1)
ew.q12$XOM <- cumprod(ew.q12$XOM.Ret+1)
ew.q12$NLY <- cumprod(ew.q12$NLY.Ret+1)
ew.q12$EWPort<-(ew.q12$ASML+ew.q12$CRM+ew.q12$XOM+ew.q12$NLY)/4
ew.q12$EWRet<-rbind(ew.q12$EWPort[1]-1,Delt(ew.q12$EWPort)[-1,])
#Q13
ew.q13 <- subset(multi_eq, index(multi_eq) > "2010-01-01")
ew.q13 <- subset(ew.q13, index(ew.q13) < "2010-03-31")
ew.q13[c(1:4,nrow(ew.q13)),]
ew.q13$ASML <- cumprod(ew.q13$ASML.Ret+1)
ew.q13$CRM <- cumprod(ew.q13$CRM.Ret+1)
ew.q13$XOM <- cumprod(ew.q13$XOM.Ret+1)
ew.q13$NLY <- cumprod(ew.q13$NLY.Ret+1)
ew.q13$EWPort<-(ew.q13$ASML+ew.q13$CRM+ew.q13$XOM+ew.q13$NLY)/4
ew.q13$EWRet<-rbind(ew.q13$EWPort[1]-1,Delt(ew.q13$EWPort)[-1,])
#Q14
ew.q14 <- subset(multi_eq, index(multi_eq) > "2010-04-01")
ew.q14 <- subset(ew.q14, index(ew.q14) < "2010-06-30")
ew.q14[c(1:4,nrow(ew.q14)),]
ew.q14$ASML <- cumprod(ew.q14$ASML.Ret+1)
ew.q14$CRM <- cumprod(ew.q14$CRM.Ret+1)
ew.q14$XOM <- cumprod(ew.q14$XOM.Ret+1)
ew.q14$NLY <- cumprod(ew.q14$NLY.Ret+1)
ew.q14$EWPort<-(ew.q14$ASML+ew.q14$CRM+ew.q14$XOM+ew.q14$NLY)/4
ew.q14$EWRet<-rbind(ew.q14$EWPort[1]-1,Delt(ew.q14$EWPort)[-1,])
#Q15
ew.q15 <- subset(multi_eq, index(multi_eq) > "2010-07-01")
ew.q15 <- subset(ew.q15, index(ew.q15) < "2010-09-30")
ew.q15[c(1:4,nrow(ew.q15)),]
ew.q15$ASML <- cumprod(ew.q15$ASML.Ret+1)
ew.q15$CRM <- cumprod(ew.q15$CRM.Ret+1)
ew.q15$XOM <- cumprod(ew.q15$XOM.Ret+1)
ew.q15$NLY <- cumprod(ew.q15$NLY.Ret+1)
ew.q15$EWPort<-(ew.q15$ASML+ew.q15$CRM+ew.q15$XOM+ew.q15$NLY)/4
ew.q15$EWRet<-rbind(ew.q15$EWPort[1]-1,Delt(ew.q15$EWPort)[-1,])
#Q16
ew.q16 <- subset(multi_eq, index(multi_eq) > "2010-10-01")
ew.q16 <- subset(ew.q16, index(ew.q16) < "2010-12-31")
ew.q16[c(1:4,nrow(ew.q16)),]
ew.q16$ASML <- cumprod(ew.q16$ASML.Ret+1)
ew.q16$CRM <- cumprod(ew.q16$CRM.Ret+1)
ew.q16$XOM <- cumprod(ew.q16$XOM.Ret+1)
ew.q16$NLY <- cumprod(ew.q16$NLY.Ret+1)
ew.q16$EWPort<-(ew.q16$ASML+ew.q16$CRM+ew.q16$XOM+ew.q16$NLY)/4
ew.q16$EWRet<-rbind(ew.q16$EWPort[1]-1,Delt(ew.q16$EWPort)[-1,])
#Q17
ew.q17 <- subset(multi_eq, index(multi_eq) > "2011-01-01")
ew.q17 <- subset(ew.q17, index(ew.q17) < "2011-03-31")
ew.q17[c(1:4,nrow(ew.q17)),]
ew.q17$ASML <- cumprod(ew.q17$ASML.Ret+1)
ew.q17$CRM <- cumprod(ew.q17$CRM.Ret+1)
ew.q17$XOM <- cumprod(ew.q17$XOM.Ret+1)
ew.q17$NLY <- cumprod(ew.q17$NLY.Ret+1)
ew.q17$EWPort<-(ew.q17$ASML+ew.q17$CRM+ew.q17$XOM+ew.q17$NLY)/4
ew.q17$EWRet<-rbind(ew.q17$EWPort[1]-1,Delt(ew.q17$EWPort)[-1,])
#Q18
ew.q18 <- subset(multi_eq, index(multi_eq) > "2011-04-01")
ew.q18 <- subset(ew.q18, index(ew.q18) < "2011-06-30")
ew.q18[c(1:4,nrow(ew.q18)),]
ew.q18$ASML <- cumprod(ew.q18$ASML.Ret+1)
ew.q18$CRM <- cumprod(ew.q18$CRM.Ret+1)
ew.q18$XOM <- cumprod(ew.q18$XOM.Ret+1)
ew.q18$NLY <- cumprod(ew.q18$NLY.Ret+1)
ew.q18$EWPort<-(ew.q18$ASML+ew.q18$CRM+ew.q18$XOM+ew.q18$NLY)/4
ew.q18$EWRet<-rbind(ew.q18$EWPort[1]-1,Delt(ew.q18$EWPort)[-1,])
#Q19
ew.q19 <- subset(multi_eq, index(multi_eq) > "2011-07-01")
ew.q19 <- subset(ew.q19, index(ew.q16) < "2011-09-30")
ew.q16[c(1:4,nrow(ew.q16)),]
ew.q19$ASML <- cumprod(ew.q19$ASML.Ret+1)
ew.q19$CRM <- cumprod(ew.q19$CRM.Ret+1)
ew.q19$XOM <- cumprod(ew.q19$XOM.Ret+1)
ew.q19$NLY <- cumprod(ew.q19$NLY.Ret+1)
ew.q19$EWPort<-(ew.q19$ASML+ew.q19$CRM+ew.q19$XOM+ew.q19$NLY)/4
ew.q19$EWRet<-rbind(ew.q19$EWPort[1]-1,Delt(ew.q19$EWPort)[-1,])
#Q16
ew.q20 <- subset(multi_eq, index(multi_eq) > "2011-10-01")
ew.q20 <- subset(ew.q20, index(ew.q20) < "2011-12-31")
ew.q20[c(1:4,nrow(ew.q20)),]
ew.q20$ASML <- cumprod(ew.q20$ASML.Ret+1)
ew.q20$CRM <- cumprod(ew.q20$CRM.Ret+1)
ew.q20$XOM <- cumprod(ew.q20$XOM.Ret+1)
ew.q20$NLY <- cumprod(ew.q20$NLY.Ret+1)
ew.q20$EWPort<-(ew.q20$ASML+ew.q20$CRM+ew.q20$XOM+ew.q20$NLY)/4
ew.q20$EWRet<-rbind(ew.q20$EWPort[1]-1,Delt(ew.q20$EWPort)[-1,])
ew.all<- rbind(ew.q1,ew.q2,ew.q3,ew.q4,ew.q5,ew.q6,ew.q7,ew.q8,ew.q9,ew.q10,
ew.q11,ew.q12, ew.q13,ew.q14,ew.q15,ew.q16,ew.q17,ew.q18,ew.q19,ew.q20)

ew.all$total_sum <- rowSums(ew.all[, -1], na.rm = TRUE)
plot(ew.all$total_sum)
```

# Create a value-weighted portfolio (rebalance each quarter) {#section-3-2}
```{r, echo=FALSE}

port <- data.ASML[,c(4,5)]
port <- merge(port,data.CRM[,c(4,5)])
port <- merge(port,data.NLY[,c(4,5)])
port <- merge(port,data.XOM[,c(4,5)])
port$ASML.ret <- Delt(port$ASML.Adjusted)
port$CRM.ret <- Delt(port$CRM.Adjusted)
port$NLY.ret <- Delt(port$NLY.Adjusted)
port$XOM.ret <- Delt(port$XOM.Adjusted)
port <- cbind(data.frame(index(port)),
              data.frame(port))
names(port)[1] <- paste("date")
port[c(1:3,nrow(port)),] 
vwport <- port[,c(1,2,4,6,8,10:13)]
vwport[c(1:3,nrow(vwport)),]
rownames(vwport) <- seq(1:nrow(vwport))

vwport$ASML.ret <- 1+vwport$ASML.ret
vwport$CRM.ret <- 1+vwport$CRM.ret
vwport$NLY.ret <- 1+vwport$NLY.ret
vwport$XOM.ret <- 1+vwport$XOM.ret
date <- seq(as.Date("2007-01-01"),as.Date("2011-12-31"),by=1)
date <- data.frame(date)

PRICE.qtr <- vwport[,c(1,2,3,4,5)]
PRICE.qtr[c(1:3,nrow(PRICE.qtr)),]
PRICE.qtr <- na.locf(merge(x=date,y=PRICE.qtr,by="date",all.x=TRUE))
PRICE.qtr <- subset(PRICE.qtr,
                    PRICE.qtr$date==as.Date("2007-01-05") |
                    PRICE.qtr$date==as.Date("2007-03-31") |
                    PRICE.qtr$date==as.Date("2007-06-30") |
                    PRICE.qtr$date==as.Date("2007-09-30") |
                    PRICE.qtr$date==as.Date("2008-01-01") |
                    PRICE.qtr$date==as.Date("2008-03-31") |
                    PRICE.qtr$date==as.Date("2008-06-30") |
                    PRICE.qtr$date==as.Date("2008-09-30") |
                    PRICE.qtr$date==as.Date("2009-01-01") |
                    PRICE.qtr$date==as.Date("2009-03-31") |
                    PRICE.qtr$date==as.Date("2009-06-30") |
                    PRICE.qtr$date==as.Date("2009-09-30") |
                    PRICE.qtr$date==as.Date("2010-01-01") |
                    PRICE.qtr$date==as.Date("2010-03-31") |
                    PRICE.qtr$date==as.Date("2010-06-30") |
                    PRICE.qtr$date==as.Date("2010-09-30") |
                    PRICE.qtr$date==as.Date("2011-01-01") |
                    PRICE.qtr$date==as.Date("2011-03-31") |
                    PRICE.qtr$date==as.Date("2011-09-30") |
                    PRICE.qtr$date==as.Date("2011-12-31") )

PRICE.qtr$ASML.shout<- c(322630000,322630000,322630000,322630000, 
                        333000000,333000000,333000000,333000000,
                        334000000,334000000,334000000,334000000,
                        334000000,334000000,334000000,334000000,
                        332000000,332000000,332000000,332000000)
PRICE.qtr$CRM.shout <- c(470000000,470000000,470000000,470000000,
                         467000000,471000000,472000000,473000000,
                         449000000,472000000,473000000,480000000,
                         481000000,481100000,481100000,481100000,
                         481200000,481200000,481300000,481500000)
PRICE.qtr$NLY.shout <- c(138000000,144000000,140000000,153000000,
                         156000000,198000000,207000000,237000000,
                         219000000,253000000,244000000,249000000,
                         251000000, 249000000,249000000,239000000,
                         249000000,237000000,237000000, 247000000)
PRICE.qtr$XOM.shout <- c(48400000,47300000,47200000,50000000,
                         48900000,49700000,49100000,48400000,
                         48700000,47100000,46500000, 45900000,
                         46200000,44800000,44300000,43900000,
                         44100000, 43200000,42900000,42600000)
weights <- PRICE.qtr
weights$ASML.mcap <- weights$ASML.Close*weights$ASML.shout
weights$CRM.mcap <- weights$CRM.Close*weights$CRM.shout
weights$NLY.mcap <- weights$NLY.Close*weights$NLY.shout
weights$XOM.mcap <- weights$XOM.Close*weights$XOM.shout

weights$tot.mcap <- rowSums(weights[10:13])
weights
weights$ASML.wgt <- weights$ASML.mcap/weights$tot.mcap
weights$CRM.wgt <- weights$CRM.mcap/weights$tot.mcap
weights$NLY.wgt <- weights$NLY.mcap/weights$tot.mcap
weights$XOM.wgt <- weights$XOM.mcap/weights$tot.mcap

WEIGHT <- weights[,c(1,15:18)]
WEIGHT
WEIGHT$date <- WEIGHT$date+1
WEIGHT
vwret <- na.locf(merge(date,WEIGHT,by="date",all.x=TRUE))
#Q1
q1.vw.wgt <- subset(vwret,vwret$date==as.Date("2007-03-31"))
Q1.pie.values <- as.numeric(q1.vw.wgt[,-1])
Q1.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q1.pie.values*100)
Q1.pie.labels <- paste(Q1.pie.labels,pct) #Add pct
Q1.pie.labels <- paste(Q1.pie.labels,"%",sep="") #Add % sign
Q1.pie.values
pie(Q1.pie.values,
    labels=Q1.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q1 Value Weigthing")
#Q2
q2.vw.wgt <- subset(vwret,vwret$date==as.Date("2007-06-30"))
Q2.pie.values <- as.numeric(q2.vw.wgt[,-1])
Q2.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q2.pie.values*100)
Q2.pie.labels <- paste(Q2.pie.labels,pct) #Add pct
Q2.pie.labels <- paste(Q2.pie.labels,"%",sep="") #Add % sign
Q2.pie.values
pie(Q1.pie.values,
    labels=Q2.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q2 Value Weigthing")
#Q3
q3.vw.wgt <- subset(vwret,vwret$date==as.Date("2007-09-30"))
Q3.pie.values <- as.numeric(q3.vw.wgt[,-1])
Q3.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q2.pie.values*100)
Q3.pie.labels <- paste(Q3.pie.labels,pct) #Add pct
Q3.pie.labels <- paste(Q3.pie.labels,"%",sep="") #Add % sign
Q3.pie.values
pie(Q1.pie.values,
    labels=Q3.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q3 Value Weigthing")
#Q4
q4.vw.wgt <- subset(vwret,vwret$date==as.Date("2008-01-01"))
Q4.pie.values <- as.numeric(q4.vw.wgt[,-1])
Q4.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q4.pie.values*100)
Q4.pie.labels <- paste(Q4.pie.labels,pct) #Add pct
Q4.pie.labels <- paste(Q4.pie.labels,"%",sep="") #Add % sign
Q4.pie.values
pie(Q1.pie.values,
    labels=Q2.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q4 Value Weigthing")
#Q5
q5.vw.wgt <- subset(vwret,vwret$date==as.Date("2008-03-31"))
Q5.pie.values <- as.numeric(q5.vw.wgt[,-1])
Q5.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q5.pie.values*100)
Q5.pie.labels <- paste(Q5.pie.labels,pct) #Add pct
Q5.pie.labels <- paste(Q5.pie.labels,"%",sep="") #Add % sign
Q5.pie.values
pie(Q5.pie.values,
    labels=Q5.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q5 Value Weigthing")
#Q6
q6.vw.wgt <- subset(vwret,vwret$date==as.Date("2008-06-30"))
Q6.pie.values <- as.numeric(q6.vw.wgt[,-1])
Q6.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q6.pie.values*100)
Q6.pie.labels <- paste(Q6.pie.labels,pct) #Add pct
Q6.pie.labels <- paste(Q6.pie.labels,"%",sep="") #Add % sign
Q6.pie.values
pie(Q6.pie.values,
    labels=Q6.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q6 Value Weigthing")
#Q7
q7.vw.wgt <- subset(vwret,vwret$date==as.Date("2008-09-30"))
Q7.pie.values <- as.numeric(q7.vw.wgt[,-1])
Q7.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q7.pie.values*100)
Q7.pie.labels <- paste(Q7.pie.labels,pct) #Add pct
Q7.pie.labels <- paste(Q7.pie.labels,"%",sep="") #Add % sign
Q7.pie.values
pie(Q7.pie.values,
    labels=Q7.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q7 Value Weigthing")
#Q8
q8.vw.wgt <- subset(vwret,vwret$date==as.Date("2008-09-30"))
Q8.pie.values <- as.numeric(q8.vw.wgt[,-1])
Q8.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q8.pie.values*100)
Q8.pie.labels <- paste(Q8.pie.labels,pct) #Add pct
Q8.pie.labels <- paste(Q8.pie.labels,"%",sep="") #Add % sign
Q8.pie.values
pie(Q8.pie.values,
    labels=Q8.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q8 Value Weigthing")
#Q9
q9.vw.wgt <- subset(vwret,vwret$date==as.Date("2009-01-01"))
Q9.pie.values <- as.numeric(q9.vw.wgt[,-1])
Q9.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q9.pie.values*100)
Q9.pie.labels <- paste(Q9.pie.labels,pct) #Add pct
Q9.pie.labels <- paste(Q9.pie.labels,"%",sep="") #Add % sign
Q9.pie.values
pie(Q9.pie.values,
    labels=Q9.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q9 Value Weigthing")




#Q10
q10.vw.wgt <- subset(vwret,vwret$date==as.Date("2009-03-30"))
Q10.pie.values <- as.numeric(q10.vw.wgt[,-1])
Q10.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q10.pie.values*100)
Q10.pie.labels <- paste(Q10.pie.labels,pct) #Add pct
Q10.pie.labels <- paste(Q10.pie.labels,"%",sep="") #Add % sign
Q10.pie.values
pie(Q10.pie.values,
    labels=Q10.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q10 Value Weigthing")

#Q11
q11.vw.wgt <- subset(vwret,vwret$date==as.Date("2008-06-30"))
Q11.pie.values <- as.numeric(q11.vw.wgt[,-1])
Q11.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q11.pie.values*100)
Q11.pie.labels <- paste(Q11.pie.labels,pct) #Add pct
Q11.pie.labels <- paste(Q11.pie.labels,"%",sep="") #Add % sign
Q11.pie.values
pie(Q11.pie.values,
    labels=Q11.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q11 Value Weigthing")

#Q12
q12.vw.wgt <- subset(vwret,vwret$date==as.Date("2009-09-30"))
Q8.pie.values <- as.numeric(q8.vw.wgt[,-1])
Q8.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q8.pie.values*100)
Q8.pie.labels <- paste(Q8.pie.labels,pct) #Add pct
Q8.pie.labels <- paste(Q8.pie.labels,"%",sep="") #Add % sign
Q8.pie.values
pie(Q8.pie.values,
    labels=Q8.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q8 Value Weigthing")

#Q13
q13.vw.wgt <- subset(vwret,vwret$date==as.Date("2010-01-01"))
Q13.pie.values <- as.numeric(q13.vw.wgt[,-1])
Q13.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q13.pie.values*100)
Q13.pie.labels <- paste(Q13.pie.labels,pct) #Add pct
Q13.pie.labels <- paste(Q13.pie.labels,"%",sep="") #Add % sign
Q13.pie.values
pie(Q13.pie.values,
    labels=Q13.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q13 Value Weigthing")

#Q14
q14.vw.wgt <- subset(vwret,vwret$date==as.Date("2011-03-31"))
Q14.pie.values <- as.numeric(q14.vw.wgt[,-1])
Q14.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q14.pie.values*100)
Q14.pie.labels <- paste(Q14.pie.labels,pct) #Add pct
Q14.pie.labels <- paste(Q14.pie.labels,"%",sep="") #Add % sign
Q14.pie.values
pie(Q14.pie.values,
    labels=Q14.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q14 Value Weigthing")
#Q15
q15.vw.wgt <- subset(vwret,vwret$date==as.Date("2010-06-30"))
Q15.pie.values <- as.numeric(q15.vw.wgt[,-1])
Q15.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q15.pie.values*100)
Q15.pie.labels <- paste(Q15.pie.labels,pct) #Add pct
Q15.pie.labels <- paste(Q15.pie.labels,"%",sep="") #Add % sign
Q15.pie.values
pie(Q15.pie.values,
    labels=Q15.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q15 Value Weigthing")
#Q16
q16.vw.wgt <- subset(vwret,vwret$date==as.Date("2011-09-30"))
Q16.pie.values <- as.numeric(q16.vw.wgt[,-1])
Q16.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q16.pie.values*100)
Q16.pie.labels <- paste(Q16.pie.labels,pct) #Add pct
Q16.pie.labels <- paste(Q16.pie.labels,"%",sep="") #Add % sign
Q16.pie.values
pie(Q16.pie.values,
    labels=Q16.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q16 Value Weigthing")
#Q17
q17.vw.wgt <- subset(vwret,vwret$date==as.Date("2011-01-01"))
Q17.pie.values <- as.numeric(q17.vw.wgt[,-1])
Q17.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q17.pie.values*100)
Q17.pie.labels <- paste(Q17.pie.labels,pct) #Add pct
Q17.pie.labels <- paste(Q17.pie.labels,"%",sep="") #Add % sign
Q17.pie.values
pie(Q17.pie.values,
    labels=Q17.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q17 Value Weigthing")
#Q18
q18.vw.wgt <- subset(vwret,vwret$date==as.Date("2011-03-31"))
Q18.pie.values <- as.numeric(q18.vw.wgt[,-1])
Q18.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q18.pie.values*100)
Q18.pie.labels <- paste(Q18.pie.labels,pct) #Add pct
Q18.pie.labels <- paste(Q18.pie.labels,"%",sep="") #Add % sign
Q18.pie.values
pie(Q18.pie.values,
    labels=Q18.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q18 Value Weigthing")
#Q19
q19.vw.wgt <- subset(vwret,vwret$date==as.Date("2011-09-30"))
Q19.pie.values <- as.numeric(q19.vw.wgt[,-1])
Q19.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q19.pie.values*100)
Q19.pie.labels <- paste(Q19.pie.labels,pct) #Add pct
Q19.pie.labels <- paste(Q19.pie.labels,"%",sep="") #Add % sign
Q19.pie.values
pie(Q19.pie.values,
    labels=Q19.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q19 Value Weigthing")
#Q20
q20.vw.wgt <- subset(vwret,vwret$date==as.Date("2011-12-31"))
Q20.pie.values <- as.numeric(q20.vw.wgt[,-1])
Q20.pie.labels <- c("ASML","CRM","NLY", "XOM")
pct <- round(Q20.pie.values*100)
Q20.pie.labels <- paste(Q20.pie.labels,pct) #Add pct
Q20.pie.labels <- paste(Q20.pie.labels,"%",sep="") #Add % sign
Q20.pie.values
pie(Q20.pie.values,
    labels=Q20.pie.labels,
    col=c("red","blue","green", "yellow"),
    main="Q20 Value Weigthing")
```