---
title: "hw3"
author: "Chun-Yu Tseng"
date: "2024-03-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part A – Risks
- 1. Using two securities from your portfolio (from different sectors) 
  * [a) Construct a variance-covariance matrix](#section-1-1)
  
## Part B – Suitable distributions for returns
- Use the same investment period and the same stocks
  * [Fit the data using GHD, HYP and NIG](#section-2-1)
  * [Plot the combined density functions](#section-2-2)
  * [Create a Q-Q plot](#section-2-3)
  * [Make a model recommendation using lik.ratio.test](#section-2-4)
  * [Calculate and plot the VaR (using all models)](#section-2-5)
  * [Calculate and plot the ES (using all models)](#section-2-6)

# Construct a variance-covariance matrix {#section-1-1}
The data I choose is ASML, XOM, and Calaucte the return in holding each stock for 5 years.
```{r Loading Data and calcuate, echo=FALSE}
library(xts)
library(quantmod)
data.ASML <- read.csv("/Users/ALEX/Documents/workspace_R/515/dataset/ASML.csv",header=TRUE)
data.XOM <- read.csv("/Users/ALEX/Documents/workspace_R/515/dataset/XOM.csv",header=TRUE)
#ASML Data
date <- as.Date(data.ASML$Date,format="%Y-%m-%d") 
data.ASML <- cbind(date, data.ASML[,-1])
data.ASML <- data.ASML[order(data.ASML$date),]
data.ASML <- xts(data.ASML[,2:7],order.by=data.ASML[,1])
names(data.ASML) <- paste(c("ASML.Open","ASML.High","ASML.Low","ASML.Close","ASML.Adjusted","ASML.Volume"))
#XOM Data
data.XOM <- cbind(date, data.XOM[,-1])  
data.XOM <- data.XOM[order(data.XOM$date),]
data.XOM <- xts(data.XOM[,2:7],order.by=data.XOM[,1])
names(data.XOM) <- paste(c("XOM.Open","XOM.High","XOM.Low","XOM.Close","XOM.Adjusted","XOM.Volume"))
#
ASML.ret <- Delt(data.ASML$ASML.Adjusted)
XOM.ret <- Delt(data.XOM$XOM.Adjusted)
#Combine two securties
returns <- cbind(ASML.ret,XOM.ret)
names(returns) <- paste(c("ASML.Ret","XOM.Ret"))
returns <- returns[-1,]
returns[c(1:3,nrow(return)),]
#Create weights of two vcetor 50% 50%
WGT.2asset <- c(0.5,0.5)
WGT.2asset <- matrix(WGT.2asset,1)
tWGT.2asset <- t(WGT.2asset)
mat.Ret <- as.matrix(returns)
head(mat.Ret)
options(scipen = "100")
cov(mat.Ret)
print ("This is the variance-covariance matrix for ASML and XOM")
VCOV.2asset <- cov(mat.Ret)*252
VCOV.2asset
```

# Fit the data using GHD, HYP and NIG {#section-2-1}
```{r echo=FALSE}
library(ghyp)
library(timeSeries)
library(fBasics)
library(FRAPO)
data.ASML <- read.csv("/Users/ALEX/Documents/workspace_R/515/dataset/ASML.csv",header=TRUE)
date <- as.Date(data.ASML$Date,format="%Y-%m-%d") 
ASMLPrice<-data.ASML$Close
str(date)
str(ASMLPrice)
ASMLRet<-returnseries(ASMLPrice)
attr(ASMLRet, 'time')<-date
datets<-as.character(date)
ASMLTimeS<-timeSeries(ASMLRet, charvec = datets)
ef<-density(ASMLTimeS, na.rm=TRUE)
plot( main = "ASML", ef)

data.XOM <- read.csv("/Users/ALEX/Documents/workspace_R/515/dataset/XOM.csv",header=TRUE)
date <- as.Date(data.XOM$Date,format="%Y-%m-%d") 
XOMPrice<-data.XOM$Close
str(date)
str(XOMPrice)
XOMRet<-returnseries(XOMPrice)
attr(XOMRet, 'time')<-date
datets<-as.character(date)
XOMTimeS<-timeSeries(XOMRet, charvec = datets)
ef_xom<-density(XOMTimeS, na.rm=TRUE)
plot( main = "XOM", ef_xom)
```

# Plot the combined density functions {#section-2-2}
```{r echo=FALSE}
#Fit the Generalized Hyperbolic Distribution
ghdfit<- fit.ghypuv(ASMLTimeS, symmetric = FALSE,silent = TRUE, control = list(maxit = 1000), na.rm = TRUE)

#Fit the Hyperbolic Distribution

hypfit<- fit.hypuv(ASMLTimeS, symmetric = FALSE,silent = TRUE, control = list(maxit = 1000), na.rm = TRUE)

#Fit the Normal Inverse Gaussian Distribution

nigfit<- fit.NIGuv(ASMLTimeS, symmetric = FALSE, silent = TRUE,control = list(maxit = 1000), na.rm = TRUE)

ghddens <- dghyp(ef$x, ghdfit)
hypdens <- dghyp(ef$x, hypfit)
nigdens <- dghyp(ef$x, nigfit)
nordens <- dnorm(ef$x, mean = mean(ASMLTimeS, na.rm=TRUE), sd = sd(c(ASMLTimeS[, 1]), na.rm=TRUE))
col.def <- c("black", "red", "blue", "green", "orange")
plot(main ="ASML", ef, xlab = "", ylab = expression(f(x)), ylim = c(0, 0.25))
lines(ef$x, ghddens, col = "red")
lines(ef$x, hypdens, col = "blue")
lines(ef$x, nigdens, col = "green")
lines(ef$x, nordens, col = "orange")

legend("topleft",
       legend = c("empirical", "GHD", "HYP", "NIG", "NORM"),
       col = col.def, lty = 1)

# XOM
ghdfit_xom<- fit.ghypuv(XOMTimeS, symmetric = FALSE, silent = TRUE, control = list(maxit = 1000), na.rm = TRUE)
hypfit_xom<- fit.hypuv(XOMTimeS, symmetric = FALSE,silent = TRUE, control = list(maxit = 1000), na.rm = TRUE)
nigfit_xom<- fit.NIGuv(XOMTimeS, symmetric = FALSE, silent = TRUE,control = list(maxit = 1000), na.rm = TRUE)

ghddens <- dghyp(ef_xom$x, ghdfit_xom)
hypdens <- dghyp(ef_xom$x, hypfit_xom)
nigdens <- dghyp(ef_xom$x, nigfit_xom)
nordens <- dnorm(ef_xom$x, mean = mean(XOMTimeS, na.rm=TRUE), sd = sd(c(XOMTimeS[, 1]), na.rm=TRUE))
col.def <- c("black", "red", "blue", "green", "orange")
plot(main ="XOM", ef, xlab = "", ylab = expression(f(x)), ylim = c(0, 0.25))
lines(ef_xom$x, ghddens, col = "red")
lines(ef_xom$x, hypdens, col = "blue")
lines(ef_xom$x, nigdens, col = "green")
lines(ef_xom$x, nordens, col = "orange")

legend("topleft",
       legend = c("empirical", "GHD", "HYP", "NIG", "NORM"),
       col = col.def, lty = 1)
```

# Create a Q-Q plot {#section-2-3}
```{r echo=FALSE}
qqghyp(ghdfit, line = TRUE, ghyp.col = "red", plot.legend = FALSE,
       gaussian = FALSE, main = "", cex = 0.8)
qqghyp(hypfit, add = TRUE, ghyp.pch = 2, ghyp.col = "blue",
       gaussian = FALSE, line = FALSE, cex = 0.8)
qqghyp(nigfit, add = TRUE, ghyp.pch = 3, ghyp.col = "green",
       gaussian = FALSE, line = FALSE, cex = 0.8)
legend("topleft", legend = c("GHD", "HYP", "NIG"),
       col = col.def[-c(1,5)], pch = 1:3)
#XOm
qqghyp(ghdfit_xom, line = TRUE, ghyp.col = "red", plot.legend = FALSE,
       gaussian = FALSE, main = "", cex = 0.8)
qqghyp(hypfit_xom, add = TRUE, ghyp.pch = 2, ghyp.col = "blue",
       gaussian = FALSE, line = FALSE, cex = 0.8)
qqghyp(nigfit_xom, add = TRUE, ghyp.pch = 3, ghyp.col = "green",
       gaussian = FALSE, line = FALSE, cex = 0.8)
legend("topleft", legend = c("GHD", "HYP", "NIG"),
       col = col.def[-c(1,5)], pch = 1:3)
```

# Make a model recommendation using lik.ratio.test {#section-2-4}
```{r echo=FALSE}
LRghdnig <- lik.ratio.test(ghdfit, nigfit)
LRghdnig
LRghdnig_2 <- lik.ratio.test(ghdfit_xom, nigfit_xom)
LRghdnig_2
```
# Calculate and plot the VaR (using all models) {#section-2-5}
```{r echo=FALSE}
p <- seq(0.001, 0.05, 0.001)
ghd.VaR <- abs(qghyp(p, ghdfit))
hyp.VaR <- abs(qghyp(p, hypfit))
nig.VaR <- abs(qghyp(p, nigfit))
nor.VaR <- abs(qnorm(p, mean = mean(ASMLTimeS, na.rm=TRUE), sd = sd(c(ASMLTimeS[, 1]), na.rm = TRUE)))
emp.VaR <- abs(quantile(x = ASMLTimeS, probs = p, na.rm=TRUE)) 
plot(main = "ASML",emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE,
     ylim = range(c(hyp.VaR, nig.VaR, ghd.VaR, nor.VaR, emp.VaR)))
box()
axis(1, at = seq(along = p), labels = names(emp.VaR), tick = FALSE)
axis(2, at = pretty(range(emp.VaR, ghd.VaR, hyp.VaR,
                          nig.VaR, nor.VaR)))
lines(seq(along = p), ghd.VaR, col = "red")
lines(seq(along = p), hyp.VaR, col = "blue")
lines(seq(along = p), nig.VaR, col = "green")
lines(seq(along = p), nor.VaR, col = "orange")
legend("topright",
       legend = c("Empirical", "GHD", "HYP", "NIG", "Normal"),
       col = col.def, lty = 1)

#xom
ghd.VaR <- abs(qghyp(p, ghdfit_xom))
hyp.VaR <- abs(qghyp(p, hypfit_xom))
nig.VaR <- abs(qghyp(p, nigfit_xom))
nor.VaR <- abs(qnorm(p, mean = mean(XOMTimeS, na.rm=TRUE), sd = sd(c(XOMTimeS[, 1]), na.rm = TRUE)))
emp.VaR <- abs(quantile(x = XOMTimeS, probs = p, na.rm=TRUE)) 
plot(main = "XOM",emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE,
     ylim = range(c(hyp.VaR, nig.VaR, ghd.VaR, nor.VaR, emp.VaR)))
box()
axis(1, at = seq(along = p), labels = names(emp.VaR), tick = FALSE)
axis(2, at = pretty(range(emp.VaR, ghd.VaR, hyp.VaR,
                          nig.VaR, nor.VaR)))
lines(seq(along = p), ghd.VaR, col = "red")
lines(seq(along = p), hyp.VaR, col = "blue")
lines(seq(along = p), nig.VaR, col = "green")
lines(seq(along = p), nor.VaR, col = "orange")
legend("topright",
       legend = c("Empirical", "GHD", "HYP", "NIG", "Normal"),
       col = col.def, lty = 1)
```

# Calculate and plot the ES (using all models) (using all models) {#section-2-6}
```{r echo=FALSE}
ghd.ES <- abs(ESghyp(p, ghdfit))
hyp.ES <- abs(ESghyp(p, hypfit))
nig.ES <- abs(ESghyp(p, nigfit))
nor.ES <- abs(mean(ASMLTimeS, na.rm=TRUE) - sd(c(ASMLTimeS[, 1]), na.rm = TRUE) *
                dnorm(qnorm(1 - p)) / p)
obs.p <- ceiling(p * length(ASMLTimeS))
emp.ES <- sapply(obs.p, function(x) abs(mean(sort(c(ASMLTimeS))[1:x])))
plot(emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE,
     ylim = range(c(hyp.ES, nig.ES, ghd.ES, nor.ES, emp.ES), na.rm = TRUE))
box()
axis(1, at = 1:length(p), labels = names(emp.VaR), tick = FALSE)
axis(2, at = pretty(range(emp.ES, ghd.ES, hyp.ES, nig.ES, nor.ES)))
lines(1:length(p), ghd.ES, col = "red")
lines(1:length(p), hyp.ES, col = "blue")
lines(1:length(p), nig.ES, col = "green")
lines(1:length(p), nor.ES, col = "orange")
legend("topright",
       legend = c("Empirical", "GHD", "HYP", "NIG", "Normal"),
       col = col.def, lty = 1)
title(main = "ASML")


#Xom
ghd.ES <- abs(ESghyp(p, ghdfit_xom))
hyp.ES <- abs(ESghyp(p, hypfit_xom))
nig.ES <- abs(ESghyp(p, nigfit_xom))
nor.ES <- abs(mean(XOMTimeS, na.rm=TRUE) - sd(c(XOMTimeS[, 1]), na.rm = TRUE) *
                dnorm(qnorm(1 - p)) / p)
obs.p <- ceiling(p * length(XOMTimeS))
emp.ES <- sapply(obs.p, function(x) abs(mean(sort(c(XOMTimeS))[1:x])))
plot(emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE,
     ylim = range(c(hyp.ES, nig.ES, ghd.ES, nor.ES, emp.ES), na.rm = TRUE))
box()
axis(1, at = 1:length(p), labels = names(emp.VaR), tick = FALSE)
axis(2, at = pretty(range(emp.ES, ghd.ES, hyp.ES, nig.ES, nor.ES)))
lines(1:length(p), ghd.ES, col = "red")
lines(1:length(p), hyp.ES, col = "blue")
lines(1:length(p), nig.ES, col = "green")
lines(1:length(p), nor.ES, col = "orange")
legend("topright",
       legend = c("Empirical", "GHD", "HYP", "NIG", "Normal"),
       col = col.def, lty = 1)
title(main = "XOM")
```